### 2020-10-21 thesis/msc-thesis.tex
add DCSS scenarios

@@

@@

\chapter{Context}

The german ministry of economy and energy recognizes that "we have long since arrived in a digitized world". This realization 
of the german government comes along with important federal and european legislation. Most prominent are DSGVO, OZG and DVG, 
modernizing data protection, governmental administration and health care.

Enterprises, organizations and authorities are required to provide digital self-service for its customers and users.
This includes for example the deletion of non-mandatory data and the digital application for unemployment benefit.

Working with existing system- and data architectures, integration of digital customer self-service solutions is necessary.

@@

This bachelor thesis explains the basis of what digital customer self-service (DCSS) is, what relevant legislation is about and how 
CSS providers can help in the digital transformation.

The technological challenge of integrating CSS providers into existing system architectures is focus of this bachelor thesis.
An integration architecture is provided which models integration of the top 10 OZG DCSS processes while satisfying DSGVO 
requirements.

The integration architecture solves the following questions:
\begin{enumerate}
     \item How can services of a CSS provider be accessed by the enterprise architecture?
     \item Which systems of a typical enterprise architecture are required?
     \item Which data objects of a typical enterprise architecture are required?
     \item Which additional systems and data objects are required?
     \item How can heterogeneous enterprise architectures be integrated the same way?
     \item How can the integration be non-invasive?
     \item How can the speed of integration development be increased?
     \item How can the speed of integration deployment be increased?
     \item How can the integration system be reliable and maintainable?
\end{enumerate}

The architecture is evaluated in respect to technological feasibility and real-life applicability. The results are incorporated into 
an operating manual, providing guidance in developing and deploying the presented integration architecture.

@@

ToDo: Briefly explain every Chapter and their relationships

\chapter{Digital Customer Self-Service (DCSS)}
This chapter introduces the concept of digital customer self-service. It defines DCSS, describes what it is by using examples and mentions benefits and challenges.

@@

It is important to distinguish between "service" and "self-Service". The difference is shown through two examples:

@@

@@

@@

\section{Challenges for Organizations}

@@

ToDo: Explain DCSS scenarios resulting from top 10 OZG processes and DSGVO

\subsection{Arbeitslosengeld 2}

\subsection{BAföG}

\subsection{Führerschein}

\subsection{Deletion of Personal Data}

\subsection{Correction of Personal Data}

\subsection{Information about collected Personal Data}

@@

ToDo: Explain what CSS Providers are (what services they can provide -> what IDAS does) and how they can help creating DCSS. 
Also explain the concept of a business connector as technological communication point of the CSS provider

@@

ToDo: Introduce Enterprise Architectures and challanges such as heterogeneous systems when trying to model them

@@

ToDo: Explain the approach of modeling enterprise architectures by EAPs and explain the used EAPs

@@

ToDo: Introduce the concept of integration. What are challenges in general and what would be an ideal integration.
Also explain the approach towards integration used (messaging, patterns)

@@

ToDo: Construct the model of the business connector

@@

ToDo: Create the integration architecture

>>>>

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\usepackage{color,soul}

@@

\listoftodos

@@

\chapter{Context}
\todo[inline, caption={Expand Context Chapter}]{Add more content to this chapter}

Digital customer self-service (DCSS) is a great tool for improving customer experience and reducing cost. Many enterprises therefore heavily
rely on it for main business services. Especially recent governmental regulations like "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung"
(DSGVO) and "Digitale Versorgung Gesetz" (DVG) have increased requirements for DCSS capabilities.

Adding DCSS to a system architecture is a common task. It usually involves integration of new DCSS components
into an existing system architecture. Due to the complicated nature of system architectures, integration proves to be a difficult
task.

One possibility for adding DCSS capabilities is the usage of solutions from DCSS providers. They keep companies and organizations up to date
with DCSS requirements and help with integration.

@@

\todo[inline, caption={Expand Objectives Chapter}]{Add more content to this chapter}

The objective of this bachelor thesis is to improve the capability of enterprises and organizations to integrate DCSS providers \hl{(or solutions?)}.
The thesis explains the basis of what DCSS and its providers are, which relevant scenarios exist and how DCSS providers can help
in the digital transformation.

The technological challenge of integrating DCSS providers into existing system architectures is focus of this bachelor thesis.

Based on governmental DCSS scenarios (due to their current relevance), an integration architecture is presented, which describes
how integration for this domain can be done. It provides information on which type of systems and data objects an existing
architecture requires in order to integrate DCSS providers. It models how CSS provider and system architecture can communicate -
deliver data and instructions. And it shows how, with fast development and deployment speed, integration can be applied to
heterogeneous system architectures, be non-invasive and reliable.

The integration architecture is evaluated in respect to technological feasibility and real-life applicability. The results are
incorporated into an operating manual, providing guidance in developing and deploying the presented integration architecture.

@@

\todo[inline, caption={Write Structure of Work Chapter}]{Briefly explain each chapter and their relationships}

\chapter{Digital Customer Self-Service (DCSS)}

\todo[inline, caption={Expand DCSS Chapter}]{Add more content to this chapter}

This chapter introduces the concept of digital customer self-service. It defines DCSS, describes what it is by usage of examples and mentions benefits such as challenges.

@@

It is important to distinguish between "service" and "self-service". The difference is shown through two examples:

@@

Customers are able to do self-service because companies provide them with self-service tools. Creating them is not trivial
and is the main business model of many companies. Video on demand websites for example do not only flourish as a result of providing access to
videos (this business model existed long before them) but as a result of the digital self-service tools they provide.

@@

\todo[inline, caption={Research Governmental Regulations Chapter}]{Explain the three regulations in general, what their purpose is what their challenges are}

@@

@@

\todo[inline, caption={Research DCSS Scenarios Chapter}]{
     \begin{enumerate}
          \item Should governmental regulations be the focus of scenarios? => good resources for OZG
     \end{enumerate}
}

Usage of DCSS OZG scenarios (\textbf{process diagrams and data schemas available}
\cite{ozgScenarios}) and DSGVO scenarios (textual description available \cite{dsgvo})

\begin{enumerate}
     \item What part of a scenario is digital?
     \item What part of a scenario can be done through a CSS provider?
     \item What part of a scenario is done through existing business systems? => new required business logic part of integration (non invasive)?
     \item What part of a scenario should be done by the integration architecture?
     \item What are commonalities of scenarios?
           \begin{enumerate}
                \item OZG scenarios often describe digital handling of applications
                \item In OZG scenarios, often multiple governmental institutions are involved. This could be modeled as one system with the problem of distributed
                      data and functionality which the integration architecture would solve.
           \end{enumerate}
\end{enumerate}

\subsection{Unemployment Benefit (AG2)}
\textbf{Available Information}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\subsection{Training Promotion (BAföG)}
\textbf{Available Information}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\subsection{Drivers License}
\textbf{Available Information}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\subsection{Company Registration and Approval}
\textbf{Available Information}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\subsection{Visa Issuance}
\textbf{Available Information}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
\end{itemize}

\subsection{Transparent Accessability}
The enterprise or organization can have the duty to make information about personal data accessible in transparent and understandable ways

\subsection{Deletion of Personal Data}
The user can have the right of removal of personal data

\subsection{Correction of Personal Data}
The user can have the right of modification of personal data.

\subsection{Information about collected Personal Data}
The user can have the right to be informed about various information of collected and stored personal data such as usage, duration of storage, ...

\subsection{Restriction of Processing}
The user can have the right to restrict the was in which personal data is processed

\subsection{Availability of Transferral of Personal Data}
The user can have the right to transfer personal data to himself or separate entity (company, organization).

@@

\todo[inline, caption={Write CSS Providers Chapter}]{Explain what CSS Providers are (what services they can provide -> what IDAS does) and how they can help creating DCSS.
Also explain the concept of a business connector as technological communication point of the CSS provider}

@@

\todo[inline, caption={Write Enterprise Architectures Chapter}]{Introduce Enterprise Architectures and challenges such as heterogeneous systems when trying to model them}

\begin{enumerate}
     \item Heterogeneous Enterprise Architecture Systems
           \begin{enumerate}
                \item Different Applications
                \item Different Application Vendors
                \item Different / No Application Interfaces
                \item Legacy Systems
           \end{enumerate}
     \item Different (proprietary) data models within and between Enterprises and Organizations
           \begin{enumerate}
                \item Different (property)name for same data objects (syntactic integration)
                \item Different meanings for same (property)name (semantic integration)
           \end{enumerate}
\end{enumerate}

@@

\todo[inline, caption={Research Relevant Systems and Data Chapter}]{Explain the approach of modeling enterprise architectures by EAPs and explain the used EAPs}

@@

\todo[inline, caption={Write Integration Chapter}]{Introduce the concept of integration. What are challenges in general and what would be an ideal integration.
Also explain the approach towards integration used (messaging, patterns)}

\begin{enumerate}
     \item Scarce Resources
           \begin{enumerate}
                \item Integration Development Speed
                      \begin{enumerate}
                           \item Necessary Development <=> Reuse of existing Technology
                           \item Complexity / Size of Integration
                      \end{enumerate}
                \item Maintenance of finished Integration
                \item Hardware / Software Costs of Integration
                      \begin{enumerate}
                           \item Licenses for Software
                           \item Scalability of Integration => Necessary Computing Power
                      \end{enumerate}
                \item Messaging Integration
                      \begin{enumerate}
                           \item Loose Coupling
                                 \begin{enumerate}
                                      \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
                                      \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
                                      \item Loose Coupling allows Reuse of "Modules" => faster development
                                 \end{enumerate}
                           \item Messaging enables communication with many systems through Adapters
                           \item Stability of Integration
                                 \begin{enumerate}
                                      \item Future Changes of EA
                                      \item Scalability
                                      \item Failure of EA or Integration Components
                                 \end{enumerate}
                           \item Messaging provides mechanisms for Stability
                                 \begin{enumerate}
                                      \item Store-and-Forward
                                      \item Load Balancing
                                 \end{enumerate}
                      \end{enumerate}
                \item Integration Patterns
                      \begin{enumerate}
                           \item Patterns speed up construction of Integration Architecture
                           \item Patterns are proven solutions
                           \item Patterns abstract from concrete technologies
                                 \begin{enumerate}
                                      \item Simplifies understanding of integration concept
                                      \item Allows implementation with different technologies
                                 \end{enumerate}
                      \end{enumerate}
           \end{enumerate}
\end{enumerate}

@@

\todo[inline, caption={Research Business Connector Chapter}]{Construct the model of the business connector}

@@

\todo[inline, caption={Integration Architecture Chapter}]{Create the integration architecture}
